### 2025-07-18 paper/sections/other/main_results.qmd
accuracy chart including synthetic data

using CTExperiments
using CTExperiments.CSV
using CTExperiments.DataFrames
using CTExperiments.Plots
using CTExperiments.StatsBase
using Random
using Serialization

@@

```{julia}
plt = CTExperiments.plot_performance(res_dir, eps=range(0.0, 0.1, length=10) |> collect, adversarial=true, byvars=["objective", "eps"]) |>
    plt -> draw(plt, figure=(size=(800, 190),), axis=(yticks=[0.0,0.5,1.0], limits=(nothing, (0,1)), xticklabelsvisible=false, xticksvisible=false))
save("paper/figures/acc.png", plt; px_per_unit=3)
```

>>>>

using CTExperiments
using CTExperiments.CairoMakie
using CTExperiments.CSV
using CTExperiments.DataFrames
using CTExperiments.Plots
using CTExperiments.StatsBase
using Random
using Serialization

@@

```{julia}
plt = CTExperiments.plot_performance(res_dir, eps=range(0.0, 0.1, length=10) |> collect, adversarial=true, byvars=["objective", "eps"], drop_synthetic=false)
plt_out = draw(plt, figure=(size=(800, 130),), axis=(yticks=[0.0,0.5,1.0], limits=(nothing, (0,1)), xticklabelsvisible=false, xticksvisible=false))
save("paper/figures/acc.png", plt_out; px_per_unit=3)
```
